---
title: "Assignment 1"
---

# Assignment 1

```{r}
1 + 1
```

My first assignment has two parts.

## (a)

## (b)

First, "polls_us_election_2016" data set is imported by the codes shown below from the dslabs package.

```{r}
install.packages("dslabs")
library(dslabs)
data(polls_us_election_2016)
```

To display the first 10 rows of the data set, we may use **head()** function. **head()** function shows the first lines (rows) of the data frame, and we can choose the number of rows we want to see.

```{r}
head(polls_us_election_2016, 10)
```

Next, total number of NA values in the entire data set is wanted to be calculated. If we want to calculate the total number of something we use **sum()** function. For this, **is.na()** will help us, too.

```{r}
total_number_na <- sum(is.na(polls_us_election_2016))
```

Now, it's wanted to replace all NA values:

-   with birth year for numeric columns,

-   with first name for character or factor columns.

Also, we will store this new data set as a new object.

```{r}
new_data_set <- polls_us_election_2016
birth_year <- 2004
first_name <- "Cerem"

for (col in names(new_data_set)) {
  if (is.numeric(new_data_set[[col]])) {
    #if the column is numeric
    new_data_set[[col]][is.na(new_data_set[[col]])] <- birth_year
     #replace NA with birth year
  }
 else if (is.character(new_data_set[[col]])) {
    #if the column is character
    new_data_set[[col]][is.na(new_data_set[[col]])] <- first_name
     #replace NA with first name
 }
  else if (is.factor(new_data_set[[col]])) {
    #if the column is factor
    levels(new_data_set[[col]]) <- c(levels(new_data_set[[col]]), first_name)
    #adding the first_name to the factor levels
    new_data_set[[col]][is.na(new_data_set[[col]])] <- first_name
    #replace NA with first name
  }
}

print(new_data_set)
 #new data set is displayed
```

Finally, we'll print the first 10 rows of the new data frame and the total number of NAs remaining in the new data frame. To do this, we'll use **head()** and **sum()** functions again.

```{r}
head(new_data_set,10)

print(new_total_number_na <- sum(is.na(new_data_set)))
```
