---
title: "Assignment 2"
code-fold: true
---

# Assignment 2

The general topic of this assignment is the IMDb Turkish Movies Overview and it consists of 4 parts. [imdb](https://m.imdb.com/search/title/) is the primer source of this assignment.

## Part 1 - URLs

In this part, movies in Turkiye which has minimum of 2500 reviews were filtered in [imdb](https://m.imdb.com/search/title/) website and it's url is saved. There was a total of 495 movies listed. After that, one more filtering was done by the movies release date: movies released from 2010 to 2023 and movies released before 2010. These urls are saved into a vector to use later.

```{r}
#| echo: true
#| message: false
#| warning: false
# Define IMDb search URLs 

imdb_url <- "https://m.imdb.com/search/title/?title_type=feature&num_votes=2500,&country_of_origin=TR"

imdb_urls_release_date <- c(
  movies_2010_to_2023 <- "https://m.imdb.com/search/title/?title_type=feature&release_date=2010-01-01,2023-12-30&num_votes=2500,&country_of_origin=TR&count=250",
  movies_before_2010 <- "https://m.imdb.com/search/title/?title_type=feature&release_date=,2009-12-31&num_votes=2500,&country_of_origin=TR&count=250"
)

# Display the vector imdb_urls_release_date
imdb_urls_release_date
```

## Part 2 - Web Scrapping

First the libraries that are needed are loaded.

```{r}
#| echo: true
#| message: false
#| warning: false
# Load required libraries
library(tidyverse)
library(rvest)
library(stringr)
library(stringi)
library(kableExtra)
```

Some helper functions are defined to use in further analysis. The reason they were created is because some data cleaning was needed to be done: 1) Title: the Turkish characters were needed to be get rid of (clean_text). 2) Duration: Durations were not in the same pattern and also they were not numeric. All of the durations turned into minutes (parse_duration). 3) Votes: Votes were not in the same pattern and also they were not numeric as in the durations. All votes turned into numeric numbers (parse_votes).

```{r}
#| echo: true
#| message: false
#| warning: false
  # Helper Functions

  #To create these functions, i've used the help of claud ai to find the proper functions that i haven't known yet. Like iconv, grepl, str_match etc. Also, i used it to give better names to these functions.

  #To convert the Turkish characters into basic ASCII characters, clean_text function is created. 
clean_text <- function(text) {
  text <- iconv(text, from = "UTF-8", to = "ASCII//TRANSLIT", sub = "")
  text <- str_trim(text)
  return(text)
}

  #To convert hours into minutes, parse_duration function is created. 
parse_duration <- function(duration) {
  if (is.na(duration)) {
    return(NA)
  }
  
  if (grepl("^\\d+h$", duration)) {
    hours <- as.numeric(gsub("h$", "", duration))
    return(hours * 60)
  }
  
  parts <- str_match(duration, "(\\d+)h (\\d+)m")
  if (is.na(parts[1])) {
    return(NA) 
  }
  hours <- as.numeric(parts[2])
  minutes <- as.numeric(parts[3])
  
  return(hours * 60 + minutes)
}

  #To clean the vote numbers, parse_votes function is created.  
parse_votes <- function(vote_str) {
  vote_str <- str_replace_all(vote_str, '["\\ ]', "") #All double quotes (") from the input string are replaced with spaces ( ).
  vote_str <- str_trim(vote_str)
  
  #Here, multiplier that is created checks if the string contains "K" or "M" using grepl. If it has "K", it'll assign the multiplier based on the suffix K, which is 1000. Same procedure works with "M", too. If there's no suffix, then it'll assign the multiplier 1, which will return the value itself. 
  # P.S. I didn't know the case_when function, i've searched for it by using chatgpt, because i wanted to learn a way to bring together those grepl functions. 
  multiplier <- case_when(
    grepl("K", vote_str) ~ 1000,
    grepl("M", vote_str) ~ 1e6,
    TRUE ~ 1
  )
  
  #After the multiplier assignment part, now all those "K", "M",  parentheses and dotes are removed & all the votes converted to numeric for the calculation that'll be made.
  vote_num <- str_replace_all(vote_str, "[()KM]", "") |>
    str_replace_all("\\.", "") |>
    as.numeric()
  
  #Finally, all the votes are returned as the correct numeric values of them.
  return(vote_num * multiplier)
}

```

The movies released from 2010 to 2023 and movies released before 2010 are combined into a one data frame with their respective Title, Year (of release), Duration (in minutes), Rating (IMDb score) and Votes by the help of functions that were mentioned before.

In the data table shown below, some of those filtered movies are displayed. As it can be seen, some of them has high ratings with their strong approval from audiences; while some of the others couldn't reached high scores.

```{r}
#| echo: true
#| message: false
#| warning: false
  # Scrape Movie Data

  #Since i've created three functions, i've decided to make the scrapping with a function, too. 
scrape_movies <- function(url) {
  page <- read_html(url)
  
  #First, a clean vector of movie titles has created.
  titles <- page |> 
    html_nodes('.ipc-title__text') |> 
    html_text() |>
    tail(-1) |>
    head(-1) |>
    sapply(clean_text) |>
    gsub("^\\d+\\.\\s*", "", x = _) |>  # Fixed this line with claud ai, there was a dot and it was causing an error, x = _ was added for the solution.
    str_trim()
  
  # For the rest of it, using almost the same pattern works.
  #Here, release years are loaded.
  years <- page |> 
    html_nodes('.sc-300a8231-7.eaXxft.dli-title-metadata-item:nth-child(1)') |> 
    html_text() |>
    str_extract("\\d{4}") |>
    as.numeric()
  
  #Here, movie durations are loaded in minutes by using the parse_duration function which was created earlier.
  durations <- page |> 
    html_nodes('.sc-300a8231-7.eaXxft.dli-title-metadata-item:nth-child(2)') |> 
    html_text() |>
    sapply(parse_duration)
  
  #Here, movie ratings are loaded.
  ratings <- page |> 
    html_nodes('.ipc-rating-star--rating') |> 
    html_text() |>
    as.numeric()
  
  #Here, votes are loaded by using the parse_votes function which was created earlier.
  votes <- page |> 
    html_nodes('.ipc-rating-star--voteCount') |> 
    html_text() |>
    sapply(parse_votes)
  
  #Here, all extracted vectors are combined into a tibble with columns:
  return(tibble(
    Title = titles,
    Year = years,
    Duration = durations,
    Rating = ratings,
    Votes = votes
  ))
}

  #To apply the scrape_movies function to each URL in the imdb_urls_release_date list, map_df was used but it kept getting error. Therefore, by the help of the claud ai, the code is updated. 
movies_df <- bind_rows(lapply(imdb_urls_release_date, scrape_movies))

knitr::kable(movies_df)
```

## Part 3 - Some Analysis

### 3.a

In this part, top 5 and bottom 5 movies were listed based on user ratings.

```{r}
#| echo: true
#| message: false
#| warning: false
top_5_movies <- movies_df |> arrange(desc(Rating)) |> head(5)
bottom_5_movies <- movies_df |> arrange(Rating) |> head(5)
```

**TOP 5 MOVIES**

```{r}
#| echo: true
#| message: false
#| warning: false
knitr::kable(top_5_movies)
```

I've watched 3 of those movies: Hababam Sinifi, Yedinci Kogustaki Mucize and Ayla. I believe all of those threes deserved high ratings, especially Hababam Sinifi. It has a few generations that really enjoy to watch it. It's like a legend. For Yedinci Kogustaki Mucize and Ayla, i'd say they were one of the best drama movies i've ever watched. I cried a lot while watching them. They touched my heart.

**BOTTOM 5 MOVIES**

```{r}
#| echo: true
#| message: false
#| warning: false
knitr::kable(bottom_5_movies)
```

I've not watched any of them, therefore i don't have many comments. I've seen some scenes from the movie Dabbe, i believe i wouldn't like that. Plus to that, lots of Turkish people love the movie Recep Ivedik but i believe i don't like this genre.

### 3.b

Here are the two of the movies i've watched before. I'm not saying they're my favorites but, since i've watched them, i've wondered their ratings. Therefore, let's see the ratings of G.O.R.A. and Issiz Adam.

```{r}
#| echo: true
#| message: false
#| warning: false
favorite_movies_of_cerem <- c("Issiz Adam", "G.O.R.A.")

favorite_movies_of_cerem_df <- movies_df |> filter(Title %in% favorite_movies_of_cerem)

knitr::kable(favorite_movies_of_cerem_df)
```

To be honest, i am not suprised by the results. 1) G.O.R.A.: It's a sci_fi comedy and i remember its popularity even though i was born in the same year that it was released. It was a funny movie, i think it deserves the 8.0 rating. 2) Issiz Adam : It's a romantic drama movie which i've found a bit boring and mundane. There are many lovers of this movie but the number of people who thinks like me are not a few. Therefore, i think the rating 6.8 is normal.

### 3.c

Audience rating is a crucial indicator of movie quality.

```{r}
#| echo: true
#| message: false
#| warning: false
library(ggplot2)
```

In this scatter plot, average ratings of Turkish movies over the years is displayed.

```{r}
#| echo: true
#| message: false
#| warning: false
  #Yearly analysis of the mean IMDB ratings in Turkiye.
yearly_ratings <- movies_df |> 
  group_by(Year) |> 
  summarise(average_rating = mean(Rating, na.rm = TRUE), Movie_Count = n())

  # Scatter plot
ggplot(yearly_ratings, aes(x = Year, y = average_rating)) +
  geom_point() +
  geom_line() +
  labs(title = "Mean IMDB Ratings Over the Years in Turkiye", x = "Year", y = "Mean IMDB Rating")
```

It can be seen that, the ratings are generally in between 6.5 and 8.5. In some years, there are no ratings since there is no movies released within the filters that we have done.

But, this plot doesn't give us enough information. Using yearly averages could be misleading due to the increasing number of movies each year.

In this bar plot, number of Turkish movies released over the years is displayed.

```{r}
#| echo: true
#| message: false
#| warning: false
  #Analysing of number of movies released in each year in Turkiye.
movies_counted <- movies_df |> 
  group_by(Year) |> 
  summarise(Movie_Count = n())

ggplot(movies_counted, aes(x = factor(Year), y = Movie_Count)) +
  geom_bar(stat = "identity") +
  labs(title = "Number of Movies Released Over the Years in Turkiye", x = "Year", y = "Number of Movies") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

It can be seen that, although the number of movies released before 2000 was very small, there seems to be an increasing trend in the number of movies released after 2000.

In this box plot, ratings (not average) of Turkish movies over the years is displayed.

```{r}
#| echo: true
#| message: false
#| warning: false
  #Box plots of ratings over the years
movies_df |>  
  group_by(Year) |> 
  ggplot(aes(x = factor(Year), y= Rating)) +
  geom_boxplot() +
  labs(title = "IMDB Ratings Over the Years in Turkiye", x = "Year", y = "IMDB Rating") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

In earlier years, ratings were concentrated in a narrow range.

After 2006, the ratings which have a wider range occured a lot.

Generally, the years which show narrow rating range have high ratings.

### 3.d

In this part, correlation between votes and ratings is analysed.

```{r}
#| echo: true
#| message: false
#| warning: false
# Correlation analysis
correlation_votes_ratings <- cor(movies_df$Votes, movies_df$Rating, use = "complete.obs")
print(paste("Correlation between Votes and Rating: ", correlation_votes_ratings))
```

This number of correlation indicates an extremely weak positive correlation, which means there’s almost no linear relationship between how many people vote on a movie and its rating.

In this scatter plot, it's displayed.

```{r}
#| echo: true
#| message: false
#| warning: false
# Scatter plot
ggplot(movies_df, aes(x = Votes, y = Rating)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "Relation between Rating and Votes", x = "Votes", y = "Rating")
```

### 3.e

In this part, correlation between durations and ratings is analysed.

```{r}
#| echo: true
#| message: false
#| warning: false
# Correlation analysis
correlation_duration_ratings <- cor(movies_df$Duration, movies_df$Rating, use = "complete.obs")
print(paste("Correlation between Duration and Rating: ", correlation_duration_ratings))
```

This number of correlation indicates a weak to moderate positive correlation, which is stronger than the correlation with vote counts we saw earlier.

In this scatter plot, it's displayed.

```{r}
#| echo: true
#| message: false
#| warning: false
# Scatter plot
ggplot(movies_df, aes(x = Duration, y = Rating)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red") +
  labs(title = "Relation between Duration and Rating", x = "Duration", y = "Rating")
```

## Part 4

In the table below, Turkish movies that are in the top 1000 movies on IMDb is shown in descending order.

```{r}
# Top 1000 Analysis
top_1000_url <- "https://www.imdb.com/search/title/?title_type=feature&groups=top_1000&country_of_origin=TR"

analyze_top_1000 <- function(url) {
  page <- read_html(url)
  
  #First, a clean vector of movie titles has created as in the scrape_movies function.
  titles <- page |> 
    html_nodes('.ipc-title__text') |> 
    html_text() |>
    tail(-1) |>
    head(-1) |>
    sapply(clean_text) |>
    gsub("^\\d+\\.\\s*", "", x = _) |>
    str_trim()
  
  #Then, releasing years are loaded in a numeric vector, again, as in the scrape_movies function.
  years <- page |> 
    html_nodes('.sc-300a8231-7.eaXxft.dli-title-metadata-item:nth-child(1)') |> 
    html_text() |>
    as.numeric()
  
  #Here, both extracted vectors are combined into a tibble with columns.
  return(tibble(
    Title = titles,
    Year = years,
  ))

}

  #analyze_top_1000 function is applied to top_1000_url, and with that, a new data frame with Turkish movies in the top 1000, containing only the title and year is created.
top_1000_df <- analyze_top_1000(top_1000_url)

  #Lastly, the duration, rating, and votes attributes of top_1000_df is filled by joining it with the original data frame, movies_df. It's named as merged_df.
  merged_df <- left_join(top_1000_df, movies_df, by = c("Title", "Year"))
  
knitr::kable(merged_df |> arrange(desc(Rating)))

```

Some movies did not make it into the top 1000, this is because IMDb filters itself by year and the 1975 movie was not included.
